\documentclass[preprint, 12pt]{elsarticle}
\usepackage{chemfig}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\setlength{\parindent}{0pt}
\usepackage{pgfplots}
\pgfplotsset{
	compat=1.3,
}
\pgfplotscreateplotcyclelist{line styles}{
	black,solid\\
	blue,dashed\\
	red,dotted\\
	orange,dashdotted\\
}

\newcommand*\GnuplotDefs{
	% set number of samples
	set samples 50;
	%
	%%% from <https://en.wikipedia.org/wiki/Normal_distribution>
	% cumulative distribution function (CDF) of normal distribution
	cdfn(x,mu,sd) = 0.5 * ( 1 + erf( (x-mu)/sd/sqrt(2)) );
	% probability density function (PDF) of normal distribution
	pdfn(x,mu,sd) = 1/(sd*sqrt(2*pi)) * exp( -(x-mu)^2 / (2*sd^2) );
	% PDF of a truncated normal distribution
	tpdfn(x,mu,sd,a,b) = pdfn(x,mu,sd) / ( cdfn(b,mu,sd) - cdfn(a,mu,sd) );
}
\usepackage{geometry}
\usepackage{mathtools}
\usepackage{tkz-berge}
\usetikzlibrary{automata}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning,shapes,shadows,arrows}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{calendar,shadings}
\renewcommand*{\familydefault}{\sfdefault}
\colorlet{winter}{blue}
\colorlet{spring}{green!60!black}
\colorlet{summer}{orange}
\colorlet{fall}{red}
\newcount\mycount

\newcommand\shapeLarge{50mm}
\newcommand\shapeMedium{25mm}
\newcommand\shapeSmall{5mm}

\newcommand*{\xMin}{0}%
\newcommand*{\xMax}{6}%
\newcommand*{\yMin}{0}%
\newcommand*{\yMax}{6}%
\newcommand*{\zMax}{6}%
\newcommand*{\zMin}{0}%

\definecolor{colorwaveA}{RGB}{98,145,224}
\definecolor{colorwaveB}{RGB}{250,250,50}
\definecolor{colorwaveC}{RGB}{25,125,25}
\definecolor{colorwaveD}{RGB}{100,100,100}
\definecolor{colorwaveE}{RGB}{80,100,1}
\definecolor{colorwaveF}{RGB}{60,1,1}
\definecolor{colorwaveG}{RGB}{25,1,100}
\definecolor{colorwaveH}{RGB}{1,90,1}
\definecolor{colorwaveI}{RGB}{1,100,1}
\definecolor{colorwaveJ}{RGB}{1,1,1}


\tikzset{%
	shapeTriangle/.style={draw,shape=regular polygon,fill=colorwaveA,circular drop shadow,regular polygon sides=3,minimum size=\shapeSmall,inner sep=0pt,outer sep=0pt},
	shapeTriangle3/.style={shapeTriangle,fill=colorwaveD,circular drop shadow,shape border rotate=45},
	shapeTriangle4/.style={shapeTriangle,fill=colorwaveA,circular drop shadow,shape border rotate=90},
	shapeTriangle5/.style={shapeTriangle,fill=colorwaveB,shape border rotate=135},
	shapeTriangle6/.style={shapeTriangle,fill=colorwaveC,shape border rotate=180},
	shapeTriangle7/.style={shapeTriangle,fill=colorwaveE,shape border rotate=225},
	shapeTriangle8/.style={shapeTriangle,fill=colorwaveF,shape border rotate=270},
	shapeTriangle9/.style={shapeTriangle,fill=colorwaveG,shape border rotate=315},
}

\tikzset{%
	shapeUgaritic/.style={draw,shape=regular polygon,fill=colorwaveD,circular drop shadow,regular polygon sides=3,minimum size=\shapeSmall,inner sep=0pt,outer sep=0pt},
}

\tikzset{%
	shapeSquare/.style={draw,shape=regular polygon,fill=colorwaveC,circular drop shadow,regular polygon sides=4,minimum size=\shapeSmall,inner sep=0pt,outer sep=0pt},
	shapeSquare2/.style={shapeSquare,shape border rotate=45},
}

\tikzset{%
	shapeHexagon/.style={draw,shape=regular polygon,fill=colorwaveA,circular drop shadow,regular polygon sides=6,minimum size=\shapeSmall,inner sep=0pt,outer sep=0pt},
	shapeHexagon2/.style={shapeHexagon,shape border rotate=90},
}

\tikzset{%
	shapeOctagon/.style={draw,shape=regular polygon,fill=colorwaveB,circular drop shadow,regular polygon sides=8,minimum size=\shapeSmall,inner sep=0pt,outer sep=0pt},
	shapeOctagon2/.style={shapeHexagon,shape border rotate=45},
}
\tikzset{%
	shapeEllipse/.style={draw,shape=ellipse,minimum size=\shapeSmall,inner sep=0pt,outer sep=0pt},
	shapeEllipse2/.style={shapeEllipse,shape border rotate=90},
}

\tikzset{%
	closedFigure/.style={draw=\draw[->,rounded corners=0.2cm,shorten >=2pt]
		(1.5,0.5)-- ++(0,-1)-- ++(1,0)-- ++(0,2)-- ++(-1,0)-- ++(0,2)-- ++(1,0)--
		++(0,1)-- ++(-1,0)-- ++(0,-1)-- ++(-2,0)-- ++(0,3)-- ++(2,0)-- ++(0,-1)--
		++(1,0)-- ++(0,1)-- ++(1,0)-- ++(0,-1)-- ++(1,0)-- ++(0,-3)-- ++(-2,0)--
		++(1,0)-- ++(0,-3)-- ++(1,0)-- ++(0,-1)-- ++(-6,0)-- ++(0,3)-- ++(2,0)--
		++(0,-1)-- ++(1,0)}
}

\tikzstyle{start}=[circle, draw=none,,minimum size=\shapeMedium, fill=blue, circular drop shadow,text centered, anchor=north, text=white]
\tikzstyle{finish}=[circle, draw=none,,minimum size=\shapeMedium, fill=blue,circular drop shadow,text centered, anchor=north, text=white]
\tikzstyle{finish}=[rectangle, draw=none, ,minimum size=\shapeMedium,fill=blue,circular drop shadow,text centered, anchor=north, text=white]

\usepackage[noadjust]{cite}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{color}
\usepackage{parskip}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{tkz-berge}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsrefs}
\usepackage{mathtools, amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tabularx,ragged2e}
\usepackage[framemethod=tikz]{mdframed}
\newcommand{\N}{\mathbb N}
\newcommand{\Q}{\mathbb Q}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section] % definitions are numbered according to sections
\newtheorem{theorem}{Theorem}[section]
\newtheorem{example}{Example}[section]
\renewcommand{\qedsymbol}{$\blacksquare$}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\renewcommand{\rmdefault}{ptm} 

\graphicspath{{figures/}}

\begin{document}

Einstein described in the 1950s theorizing as an increased proportional allocation percentage of the “visual and motor” or “muscular” Brodmann areas than the linguistic (Einstein 1952, p. 43) areas.\cite{key1}.  Here are some hypothetical observations on spatial intelligence for the human species:

\begin{enumerate} \itemsep -2pt
\item Human males higher spatial ability in right hemisphere and use rotational imagery in working memory.  \cite{key2} 
\item Spatial Intelligence is hypothesized to promote deeper understanding of the material.  \cite{key1} 
\item Navigational structure in hippocampus and spatial processing gender specific in female cortical areas.  Both vision and auditory systems are used for navigation.  \cite{key2} 
\item The parietal cortex area has space perception and hippocampus for memory formation foundation spatial processing in spatial intelligence.  Gender specific with a larger area in human males.  \cite{key2} 
\item Inferior Pareital lobe (IPL) involved in sensory acquisition and selective attention and mathematical ability.  The lateralization of IPL generates time, speed, and rotation in the left, spatial and the relationship between right body parts.  \cite{key2} 
\item Visually and Auditory guided movement requires cortical lateralization.\cite{key2} 
\item Differences in  navigational preference neuroanatomical features based genders in humans.  Human males the left hippocampus regions emphasis on opposites and distances and human females landmarks, past representations of both vision and sound together with cerebral cortex.  \cite{key2} 
\item Navigation through visual mazes or patterns with human genders is hypothesized with right and left hippocampus with human males the left and human females use the right prefrontal cortex.  \cite{key2} 
\item Cerebellum is larger in in human males proportionally with larger mass required for motor control. \cite{key2}
\item There is a difference in computational speed with white and grey matter in the human species. \cite{key2}
\end{enumerate}

\bibliographystyle{plain}
\begin{thebibliography}{00}

\bibitem[1]{key1} Einstein, Albert. (1952) 
\newblock “Letter to Jacques Hadamard.” In The Creative Process, edited by Brewster Ghiselin, 
\newblock pp. 43–44. Berkeley, Calif.: University of California Press, 1952. 

\bibitem[2]{key2} Zeenat Zaidi.(2010)
\newblock Gender Differences in Human Brain: A Review.
\newblock The Open Anatomy Journal 2:37-55.

\end{thebibliography}

\end{document}
